Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-28 paper/paper.tex
Comments on the algorithm definition

\begin{lemma} \label{lemma:k=3}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{lemma}

@@

   Let \emph{Arb-partition} be the algorithm that moves to an arbitrary perfect partition
on each inter-cluster request.
\begin{theorem}
	Algorithm \emph{Arb-partition} is $O(\ell)$-competitive when $k=3$.
\end{theorem}

>>>>

Let \emph{Arb-partition} be the algorithm that moves to an arbitrary perfect partition
on each inter-cluster request.

\maciek{The definition of the algorithm should be: it moves to an arbitrary perfect partition that is the closest from the current partition.}
\maciek{Therefore, I would name it differently. The easiest would be to call it "greedy" with an explaination what we mean. Alternatives: CPP (closest perfect partition)}

\begin{lemma} \label{lemma:k=3}
  The rebalancing cost for the Arb-partition algorithm for $k=3$ is $O(1)$.
  %\maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{lemma}

@@

\begin{theorem}
	Algorithm \emph{Arb-partition} is $O(\ell)$-competitive when $k=3$.
\end{theorem}
